The Name of the Title is Hope

### 2019-03-26 emsoft-2019/main.tex
fix problem description

\section{Introduction}
\section{Background}
\subsection{Robust MPC}
\subsection{Finite Precision Arithmetic}
\subsection{Daisy}
\section{Problem Description}
In this work we present an innovative method for the off-line design of robust MPC controllers (explicit), for linear time invariant systems.

To guarantee stability of the system at runtime, at design time the designer specifies the maximal disturbance value the system can tolerate: we call this numeric value \texttt{delta}.

\texttt{delta} has to be an upper bound for both errors generated by the system itself (e.g. noise from sensors) and disturbance coming from sources external to the system (e.g. friction).

The system is then designed to be robust against any kind of disturbance up to a maximal value \texttt{delta}.

Among the sources of disturbance targeting the controller, our goal is to assure that the approximation error caused by the use of finite precision arithmetic is also bounded by this design property.

Given an initial delta, we find the right controller for a system by solving an off-line optimization problem. We rely on MATLAB multi-parametric toolbox to solve such optimization problem~\cite{matlabMPT, matlabYALMIP}. 
The output of the suite is a continuous piecewise affine (PWA) function, together with a partitioning of the domain of \statevarmath. Each element in the partitioning is called a region.
A generic region $i$ consists in a n-polytope, uniquely identified by a set of inequalities in the form: $H_{i}\statevar<=K_{i}$.

We call \statespace\space the union of all regions $i$ is the domain of the state variable $x_{k}$:
\begin{equation}
\statespace = \bigcup_{i}(H_{i}\statevar<=K_{i})
\end{equation}

@@

>>>>

\section{Introduction}
\section{Background}
\subsection{Robust MPC}
\subsection{Finite Precision Arithmetic}
\subsection{Daisy}
\section{Problem Description}
In this work we present an innovative method for the off-line design (explicit) of robust MPC controllers for linear time invariant systems.

Consider the (discrete) state space model:
\begin{flalign}\label{eq:statespacemodel}
& x_{k+1} = A\statevar + Bu_{k}
%& y_{k} = C\statevar\nonumber
\end{flalign}

where $\statevar\in\mathbb{R}_{n}$ is the state variable at time $k$, $u_{k}$ is the scalar control input, and $A\in\mathbb{R}^{nxn}$ and $B\in\mathbb{R}^{n}$ guarantee the stability of the system at runtime.

The controller $u_{k}$ for (\ref{eq:statespacemodel}) is found by solving an off-line optimization problem. We rely on MATLAB multi-parametric toolbox to solve such optimization problem~\cite{matlabMPT, matlabYALMIP}. 
The output of the suite is a continuous piecewise affine (PWA) function, together with a partitioning of the domain of \statevarmath. Each element in the partitioning is called region.
A generic region $i$ consists in a n-polytope, uniquely identified by a set of inequalities in the form: $H_{i}\statevar<=K_{i}$.

We call \statespace\space the union of all regions $X_{i}$ in the domain of the state variable $x_{k}$:
\begin{equation}
\statespace = \bigcup_{i}(H_{i}\statevar<=K_{i})
\end{equation}

@@

At design time, the designer specifies the maximal disturbance value the controller can tolerate: we call this numerical value \texttt{delta}.

\texttt{delta} has to be an upper bound for both errors generated by the system itself (e.g. noise from sensors) and disturbance coming from sources external to the system (e.g. friction). The controller is then designed to be robust against any kind of disturbance up to a maximal value \texttt{delta}.

Among the sources of disturbance targeting the output of the controller, our goal is to assure that the approximation error caused by the use of finite precision arithmetic is also bounded by this design property.
